\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-11-02 slides/gvn-hoist.tex
algorithm overview
vn and insertion points

>>>>

\frame{\frametitle{\GVN{}-Hoist: Algorithm}
  \begin{itemize}
  \item dfs number all instructions
  \item compute value number of scalars, loads, stores, calls
  \item compute insertion points of each type of instructions separately
  \item hoist expressions
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-collecting value numbers}
  \begin{itemize}
  \item For loads value number the pointer operand
  \item For stores value number the pointer operand and the value being stored
  \item For calls, scalars use the GVN infrastructure
  \end{itemize}
}

\frame{\frametitle{\GVN{}-Hoist: Algorithm-compute insertion points}
  \begin{itemize}
  \item For a set of instructions having the same value number, compute a common insertion point.
  \item When no common insertion points can be found, partition the candidates into a smaller set of
    hoistable candidates.
  \item Partition such that instructions with closeby DFS numbers are together.
  \end{itemize}
}
